Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs

### 2025-03-27 src/tex/ms.tex
Manuscript updates

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.24$. {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio}
    \label{fig:ofe-df}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$. {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
    \label{fig:ofe-distribution-parameters}
\end{figure*}
